Build Your Own EV: A Rapid Energy-Aware Synthesis of Electric Vehicles

### 2018-07-31 draft/draft.tex
Grant ACK is still missing.
Author
ACK 업데이트

\author{
	Naehyuck~Chang,~\IEEEmembership{Fellow,~IEEE} and
	Donkyu~Baek,~\IEEEmembership{Member,~IEEE,}
\thanks{Direct questions and comments about this article to Naehyuck Chang, Korea Advanced Institute of Science and Technology, 291, Daehak-ro, Yuseong-gu, Daejeon, Korea (e-mail: naehyuck@cad4x.kaist.ac.kr).}
}

>>>>

\author{
	Donkyu~Baek,~\IEEEmembership{Member,~IEEE,}
	Jaemin~Kim,~\IEEEmembership{Member,~Student IEEE} and
	Naehyuck~Chang,~\IEEEmembership{Fellow,~IEEE}

\thanks{Direct questions and comments about this article to Naehyuck Chang, Korea Advanced Institute of Science and Technology, 291, Daehak-ro, Yuseong-gu, Daejeon, Korea (e-mail: naehyuck@cad4x.kaist.ac.kr). This work is supported in part by NRF Grant 2015R1A2A1A09005694.}
}
